---
title: "bike"
author: "Thomas Dang"
date: "April 8, 2017"
output: pdf_document
---

First we perform a general linear regression and locate which predictors are good for our response variable 'cnt'.

Once we find these predictors, we can then move them to a different dataset known as small_bike.
```{r}
#==================================================#
#===THIS SECTION OUTLINES THE BIKE DATASET OUTPUT==#
#==================================================#
library(readr)
bike <- read_csv("hour.csv")
head(bike)
names(bike)
model1 <- lm(cnt ~., data=bike)
summary(model1)
small_bike = bike[c(3,6,9,10,11,17)]  
names(small_bike)
```

Here we perform linear regression on the training set. The accuracy is only 56%.
```{r}
#===LINEAR REGRESSION===
set.seed(1234)
i <- sample(2, nrow(small_bike), replace=TRUE, prob=c(0.8, 0.2))
bike.train <- small_bike[i==1,]
bike.test <- small_bike[i==2,]
lm1 <- lm(bike.train$cnt~., data=bike.train)
lm1.pred <- predict(lm1, newdata=bike.test)
cor(lm1.pred, bike.test$cnt)
```

Next we perform knn regression on the training set. We get a big improvement of 90% on this model.
```{r}
#===KNN REGRESSION===
library(caret)
fit <- knnreg(bike.train[,1:5],bike.train$cnt,k=10)
predictions <- predict(fit, bike.test[,1:5])
cor(predictions, bike.test$cnt)
```

Finally we make a decision tree on the dataset. We get the summary and tree model as our outputs. We also see that the square root of the Mean Squared Error is about 73.3%, meaning that the decision tree isn't as accurate as the knn regression model but more accurate
than linear regression.
```{r}
#===DECISION TREE===
library(tree)
library(MASS)
set.seed(1234)
train = sample(1:nrow(small_bike), nrow(small_bike)/2)
tree.bike = tree(cnt~., small_bike, subset=train)
summary(tree.bike)
plot(tree.bike)
text(tree.bike, pretty=0)
cv.bike = cv.tree(tree.bike)
plot(cv.bike$size, cv.bike$dev, type='b')
prune.bike = prune.tree(tree.bike, best=5)
plot(prune.bike)
text(prune.bike, pretty=0)
yhat = predict(tree.bike, newdata=small_bike[-train,])
bike.test = small_bike[-train,"cnt"]
mean((((yhat-bike.test))^2)^0.5)
```

